Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2015-01-20 AO_bondedSi.tex
break out the tables into \input{} in their own files

\subsection{Predicted transmission spectrum for bonded Si with finite interface gap}
\label{secTheory}
A pair of bonded silicon wafers or pucks with a small gap actually forms there coupled cavities with the air gap as the the central cavity.  The outer cavities, those within the Si, however, were not produced with coherence in mind.  Their sides are not necessarily flat and parallel to the required level and the specifics of their deviation from perfect etalons are usually not known to the level necessary to treat them as oherent structures in the analysis.  The multiple internal reflections within the Si therefore present a hurdle to an analysis of the air gaps where the gap size si small enough that the cavity it forms can always be treated as a coherent structure.  Treatments for multiple coherent reflections have been described in detail in the optics literature \cite{2007fuph.book.....S}.  The wave transfer matrix technique treats each dielectric interface as a matrix with elements relating the pre- and post- interface complex amplitudes in the left and right directions.  We adapted the wave transfer technique for incoherent interactions \cite{2002ApOpt..41.3978K} to deal with the cavities within the Si.  Specifically I constructed an incoherent wave transfer matrix whose elements relate the intensities (and not complex amplitudes) before and after an interface.  The details are worked out in Appendix \ref{sec:Append-IMRTMM}.  We computed the transmission for two scenarios- first a double side polished (DSP) Si sample with no gap, and second a pair of bonded Si samples with a gap thickness $d$.  The DSP Si sample with no air gap has a transmission equal to:

@@

It is clear that in the limit $\lim_{d \rightarrow 0}$, the etalon approaches 100\% transmission.  Figure \ref{figEtalonRelTrans} shows a plot of Equation \ref{eqFP} for gap sizes, $d$, of 0, 20, 35, 60, 350, and 3500 nm.  In Section \ref{secResults} we compare wavelength dependent transmission measurements to by-eye fits of Equation \ref{eqFP}.  Depending upon the intended operating wavelength, gaps as small as 35-60 nm can cause losses comparable to or greater than the losses produced by antireflection coatings.

@@

\begin{table}[h!]
\caption{UTexas Si bonding experiments \label{tabbondexper}}
\begin{center}
    \begin{tabular}{ c c c c c c}
    \hline
    Name & Diameter & Thickness & Pattern Type & Pattern Depth & Notes \\ 
    -  & mm & mm & - & nm & - \\ 
        \hline
    HA1     & 75   & $10$ $\times$ 2& None & - & \\
    VG01   & 100 &$1$ $\times$ 2 & None  & - &  \\
    VG02   & 100 & $3.3$ $\times$ 2 &  None  & - &  \\
    VG03   & 100 & $3.3$ $\times$ 2 &  Hole \&Petal & 4000$\pm$200 & \\    
    VG04   & 100 & $1$ $\times$ 2 &  Patchwork Islands & 15$\pm7$ & \\
    VG07   & 100 & $1$ $\times$ 2 &  mesh C, M, F & 12$\pm7$ & \\ %see email from Victor on 5/16/13
    VG08   & 100 & $1$ $\times$ 2 &  mesh C, M, F & 12$\pm7$ & \\ 
    VG09   & 75   & $1$ $\times$ 2 & mesh C & 49 $\pm$6 & \\
    VG15   & 100 & $0.8$ $\times$ 2 &  mesh C, M, F  &14 $\pm$2 & \\
    VS20   & 100 & $0.8$ $\times$ 2 &  mesh C, M, F & 95 $\pm$5 & \\
    \hline
    \end{tabular}
\end{center}
\end{table}

\begin{table}[h!]
\caption{Patterned gap properties \label{tabPatternFills}}
\begin{center}
    \begin{tabular}{ c c c c }
    \hline
    Pattern name & fill factor & minimum feature size & bulk description \\ 
    - & \% & $\mu$m & - \\ 
    \hline
    Hole & 100 & - & 25 mm diameter hole \\     
    Petal & $\sim1$ & $\sim$2000 & long petal lines \\         
    Mesh F & 50 & 40 &  100 $\mu$m square holes, Fig. 
    VS20pattern}\\ 
    Mesh M & 50 & 200 &  500 $\mu$m square holes\\ 
    Mesh C & 50 & 620 &  1500 $\mu$m square holes\\     
        \hline
    \end{tabular}
\end{center}
\end{table}

@@

The Cary 5000 has four operation modes: single front, single back, double, and double reverse.  We experimented with single front and double modes.  Double mode takes a reference spectrum simultaneously with the target spectrum.  In both single and double mode, a baseline scan is taken with no sample in the measurement holder.  The baseline spectrum is the raw spectral response of the system.  We automatically divide sample spectra by the baseline spectrum.  In single beam mode, the baseline measurements must be repeated about every half hour for post-process division.  In double beam mode the front beam is automatically divided by the rear beam, which corrects out lamp luminosity drift, for example.  We estimated the uncertainty and measurement repeatability of single and double modes in the following way: we computed the RMS error and measurement repeatability in a single measurement by computing the standard deviation of a spectrum taken immediately after a baseline scan with no sample present.  We found that the mean value in single mode drifted by about 0.2\% over several measurements.  The standard deviation of the featureless spectrum was typically 0.02\% from point to point, with some portions of the spectrum demonstrating increased variance, perhaps attributable to atmospheric absorption.  In double beam mode, the spectrograph drift was much lower.  The simultaneous reference in double beam mode divides out the 0.2\% drift in the mean transmission level attributable to lamp drift that we saw in single beam measurements.  In double beam mode, the drift in mean transmission level is 0.02\%.  These values are accurate for measurements over a half hour timescale or less.  With accuracies and drift rates at this level, the curves in Figure \ref{figEtalonRelTrans} indicate that the axial extent of gaps as small as a few nm should be measurable.

@@

\begin{table}[h!]
\caption{Summary of Cary 5000 Measurement parameters \label{tab:Cary5000pars}}
\begin{center}
\begin{tabular}{ c c }
\hline
        Parameter (Units) & Value \\ 
\hline
        Spectral sampling interval (nm) & 2.0$-$10.0 \\
        Spectral resolution (nm) & 5 \\
        Time per sample (s) & 0.1 \\
        Typical measurement range (nm) & 1000-2500 \\
	Typical Single mode mean drift (\%) & 0.20 \\
 	Beam size (mm $\times$ mm) & $2 \times 8$ \\
        Directly measured linearity range (dB) & $>24$ \\
    \hline
    \end{tabular}
\end{center}
\end{table}

@@

% Table of experiments
\begin{table}[h!]
\caption{Cary5000 Experiment Log \label{tabExperiments}}
\begin{center}
    \begin{tabular}{c c c c c c c}
    \hline
	Date &  Mode  & $\Delta \lambda$ & SBW & Sampling & \# of spectra & Sample IDs \\
	\emph{mm/dd/yyyy} &  -  & nm & nm & nm & - \\
%     \hline		
%	02/04/2013 & ? & ? 				& 5.0 & 10.0 &  16 &   -  \\
%     \hline		
%	02/06/2013 & ? & ? 				& 5.0 & 10.0 &  16 &   -  \\	     
     \hline		
     	02/18/2013 & Single & 1000$-$2500 & 5.0 & 10.0 &  16 &   -  \\
     	                   &            &                       &       &         &    4 &  Baseline\\	
     	                   &            &                       &       &         &    1 &  VG01\\
	                   &            &                       &       &         &    4 &  VG02\\	                   
	                   &            &                       &       &         &    2 &  VG03\\	                   
	                   &            &                       &       &         &    2 &  VG04\\
	                   &            &                       &       &         &    2 &  VG05\\	                   
	                   &            &                       &       &         &    2 &  VG06\\
    \hline
%	05/02/2013 & Single & 1000$-$2500 & 5.0 & 5.0  &  30 &   -  \\
%     	                   &            &                       &       &         &    12 &  Baseline\\	
%     	                   &            &                       &       &         &    18 &  Other\\
%    \hline
	05/03/2013 & Single & 1000$-$2500 & 5.0 & 5.0  &  28 &   -  \\
     	                   &            &                       &       &         &    8 &  Baseline\\	
     	                   &            &                       &       &         &    1 &  VG05\\ %Consider replacing VG05 with "DSP reference sample"  or something
     	                   &            &                       &       &         &    6 &  VG03\\
     	                   &            &                       &       &         &    13 &  Other\\ %These had to do with beam size experiments
    \hline
	06/07/2013 & Mix & 1000$-$2500 & 5.0 & 5.0  &  43 &   -  \\
	                   &            &                       &       &         &    11 &  Baseline\\	                   
	                   &            &                       &       &         &    9 &  VG05\\	                   
	                   &            &                       &       &         &    7 &  VG07\\
	                   &            &                       &       &         &    6 &  VG08\\
	                   &            &                       &       &         &    4 &  HA1\\
	                   &            &                       &       &         &    6 &  other\\ % These are mostly just baselines without automatic division
    \hline
	08/02/2013 & Single & 1000$-$2500 & 5.0 & 2.0  &  17 &   -  \\	
	                   &            &                       &       &         &    3 &  Baseline\\
	                   &            &                       &       &         &    4 &  VG05\\	                   
	                   &            &                       &       &         &    2 &  VG15\\
	                   &            &                       &       &         &    2 &  VS20\\
	                   &            &                       &       &         &    6 &  VG09\\
    \hline
    	09/11/2013 & Double & 1000$-$2500 & 5.0 & 2.0  &  20 &   -  \\	                   
	                   &            &                       &       &         &    1 &  Baseline\\
	                   &            &                       &       &         &    14 &  VS21\\	                   
	                   &            &                       &       &         &    5 &  Blank\\ %This is really the same as a baseline
    \hline
    	09/16/2013 & Double & 1000$-$2500 & 5.0 & 2.0  &  21 &   -  \\
	                   &            &                       &       &         &    2 &  Baseline\\
	                   &            &                       &       &         &    7 &  VG07\\	                   
	                   &            &                       &       &         &    4 &  VG05\\	
	                   &            &                       &       &         &    4 &  VG12\\
	                   &            &                       &       &         &    2 &  VG15\\	                   
	                   &            &                       &       &         &    2 &  VG08\\
    \hline
    \end{tabular}
\end{center}
\end{table}

>>>>

\subsection{Predicted transmission spectrum for bonded Si with finite interface gap}
\label{secTheory}
A pair of bonded silicon wafers or pucks with a small gap actually forms their coupled cavities with the air gap as the the central cavity.  The outer cavities, those within the Si, however, were not produced with coherence in mind.  Their sides are not necessarily flat and parallel to the required level and the specifics of their deviation from perfect etalons are usually not known to the level necessary to treat them as oherent structures in the analysis.  The multiple internal reflections within the Si therefore present a hurdle to an analysis of the air gaps where the gap size si small enough that the cavity it forms can always be treated as a coherent structure.  Treatments for multiple coherent reflections have been described in detail in the optics literature \cite{2007fuph.book.....S}.  The wave transfer matrix technique treats each dielectric interface as a matrix with elements relating the pre- and post- interface complex amplitudes in the left and right directions.  We adapted the wave transfer technique for incoherent interactions \cite{2002ApOpt..41.3978K} to deal with the cavities within the Si.  Specifically I constructed an incoherent wave transfer matrix whose elements relate the intensities (and not complex amplitudes) before and after an interface.  The details are worked out in Appendix \ref{sec:Append-IMRTMM}.  We computed the transmission for two scenarios- first a double side polished (DSP) Si sample with no gap, and second a pair of bonded Si samples with a gap thickness $d$.  The DSP Si sample with no air gap has a transmission equal to:

@@

It is clear that in the limit $\lim_{d \rightarrow 0}$, the etalon approaches 100\% transmission.  Figure \ref{figAbsoluteTrans} shows a plot of Equation \ref{eqFP} for gap sizes, $d$, of 0, 20, 35, 60, 350, and 3500 nm.  In Section \ref{secResults} we compare wavelength dependent transmission measurements to by-eye fits of Equation \ref{eqFP}.  Depending upon the intended operating wavelength, gaps as small as 35-60 nm can cause losses comparable to or greater than the losses produced by antireflection coatings.

@@

\input{tbls/tbl_experiments.tex}

\input{tbls/tbl_meshPatterns.tex}

@@

The Cary 5000 has four operation modes: single front, single back, double, and double reverse.  We experimented with single front and double modes.  Double mode takes a reference spectrum simultaneously with the target spectrum.  In both single and double mode, a baseline scan is taken with no sample in the measurement holder.  The baseline spectrum is the raw spectral response of the system.  We automatically divide sample spectra by the baseline spectrum.  In single beam mode, the baseline measurements must be repeated about every half hour for post-process division.  In double beam mode the front beam is automatically divided by the rear beam, which corrects out lamp luminosity drift, for example.  We estimated the uncertainty and measurement repeatability of single and double modes in the following way: we computed the RMS error and measurement repeatability in a single measurement by computing the standard deviation of a spectrum taken immediately after a baseline scan with no sample present.  We found that the mean value in single mode drifted by about 0.2\% over several measurements.  The standard deviation of the featureless spectrum was typically 0.02\% from point to point, with some portions of the spectrum demonstrating increased variance, perhaps attributable to atmospheric absorption.  In double beam mode, the spectrograph drift was much lower.  The simultaneous reference in double beam mode divides out the 0.2\% drift in the mean transmission level attributable to lamp drift that we saw in single beam measurements.  In double beam mode, the drift in mean transmission level is 0.02\%.  These values are accurate for measurements over a half hour timescale or less.  With accuracies and drift rates at this level, the curves in Figure \ref{figAbsoluteTrans} indicate that the axial extent of gaps as small as a few nm should be measurable.

@@

\input{tbls/tbl_cary5000Pars.tex}

@@

\input{tbls/tbl_experimentLog.tex}
